\textbf{Computational Fuzzy Extractors}

### 2013-05-17 trunk/CompFuzzExt.tex
finished section 5

\newcommand{\ve}{\vect{e}}
\newcommand{\vm}{\vect{m}}
\newcommand{\vy}{\vect{y}}
\newcommand{\vE}{\vect{E}}
\newcommand{\vS}{\vect{S}}
\newcommand{\vA}{\vect{A}}
\newcommand{\vc}{\vect{c}}
\newcommand{\vW}{\vect{W}}
\newcommand{\vR}{\vect{R}}
\newcommand{\vU}{\vect{U}}
\newcommand{\vT}{\vect{T}}
\newcommand{\vX}{\vect{X}}
\newcommand{\vB}{\vect{B}}
\newcommand{\vz}{\vect{z}}
\newcommand{\vd}{\vect{d}}
\newcommand{\vs}{\vect{s}}
\newcommand{\vx}{\vect{x}}
\newcommand{\va}{\vect{a}}
\newcommand{\vb}{\vect{b}}
\newcommand{\vgamma}{\mathbf{\Gamma}}
\newcommand{\vt}{\vect{t}}
\newcommand{\vu}{\vect{u}}
\newcommand{\vF}{\vect{F}}
\newcommand{\recout}{x}
\newcommand{\ignore}[1]{}

\title{\textbf{Computational Fuzzy Extractors}}
\author{Benjamin Fuller%\footnote{The work of Benjamin Fuller is sponsored by the United States Air Force under Air Force Contract FA8721-05-C-0002. Opinions, interpretations, conclusions and recommendations are those of the authors and are not necessarily endorsed by the United States Government.}
 \and Xianrui Meng \and Leonid Reyzin}
\begin{document}
\maketitle

@@

\item\textbf{Positive Result:} We show that the negative result can be overcome by
analyzing computational fuzzy extractors directly.  Namely, we show
how to build a computational fuzzy extractor whose output key length
equals the entropy of the source (this is impossible in the
information-theoretic setting). Our construction is based on the
hardness of the Learning with Errors (LWE) problem, and is secure when
the noisy source is uniform or symbol-fixing (that is, each dimension
is either uniform or fixed). As part of the security proof, we show a result of independent interest, namely
that the decision version of LWE is secure even when a small number of
dimensions has no error.
\end{itemize}
\end{abstract}

\newcommand{\M}{\mathcal{M}}
\section{Introduction}\label{sec:introduction}

@@

\begin{theorem}
\label{thm:lossless secure conductor log}
Let $n$ be a security parameter and let $t = c\log n$ for some constant $c$.  Let $d\in \mathbb{Z}^+$ be a constant and consider the Hamming metric with block length $b = \log (2n^3 (c+2d)/d)$.  Let $W$ be uniform over $\zo^{(c+2d)nb/d}$.  If GAPSVP and SIVP are hard to approximate within polynomial factors~(on lattices of dimension $n/4$) using quantum algorithms, then there is a setting of $q = \poly(n)$ such that \consref{cons:informal construction} is a lossless fuzzy extractor.  That is, $H^{\hill}_{\epsilon, s_{sec}}(X_{1,..., n/2}|\vA, \vA X+W) = n/2\log q = H_\infty(W)$
% for following parameters:
%\[
%(\zo^{(c+d)/dn\log b}, |W|, \epsilon, s_{sec}, s_{sketch}, s_{rec}, t)
%\] 
with 
$\epsilon = \ngl(n), s_{sec} = \poly(n)$,  sketch runs in time $O(n^3\log n)$, and recover takes expected time $O(n^{4d+3} \log n)$ with error probability $\delta = e^{-\Omega(n)}$ over the choice of $\vA$.
\end{theorem}
\begin{proof}
Security follows by combining Lemmas~\ref{lem:uniform LWE decision} and~\ref{lem:many hardcore bits}, efficiency follows by \lemref{lem:i t poly time}.
\end{proof}

For a more detailed explanation of the various parameters and constraints see \secref{sec:parameter settings}.  In particular, we describe how to set $q = \poly(n)$.  
\thref{thm:lossless secure conductor log} shows that a computational fuzzy conductor can be built without incurring any entropy loss.  This is essentially due to $\vA X+W$ looking like a uniformly random point and providing no information about either $X$ or $W$.  
%A natural question to ask is whether security degrades gracefully when $W$ is not the uniform distribution.  We begin to provide an answer in \secref{sec:LWE block fixing sources}.

\subsection{Comparison with computational extractor based construction}
\label{sec:prg based comparison}
In this section, we constructed a computational fuzzy extractor by making the whole process ``computational.''  Alternatively, a computational fuzzy extractor could be constructed by using a computational extractor~\cite{krawczyk2010cryptographic} in place of the information-theoretic randomness extractor.  A simple example of a computational extractor is the \emph{extract-then-expand} mechanism: a pseudorandom generator is applied to the output of a information-thereotic randomness extractor. 
%using an information theoretic fuzzy extractor and then applying a pseudorandom generator to the output of the fuzzy extractor.  This is the extract-then-expand computational extractor suggested by Krawczyk in~\cite{krawczyk2010cryptographic}.  
Under the same hardness of approximating GAPSVP and SIVP, Applebaum et. al. achieve a pseudorandom generator with linear stretch~\cite{applebaum2006pseudorandom}.  They consider $\vA$ as a public value and show a setting of parameters where $f_\vA(x, e) = \vA x + e$ is a pseudorandom generator with linear stretch.  Likewise, by increasing the field size in \consref{cons:informal construction}, it is possible to output a linear factor of the number of input bits~(see \secref{sec:parameter settings}).  Both techniques are able to produce a linear stretch on the entropy of the source.

Thus, using the same assumptions as \thref{thm:lossless secure conductor log}, we can obtain a computational extractor.  This means we could  build a computational fuzzy extractor using: 1) an information-theoretic secure sketch 2) a computational extractor.
We call the paradigm of running a secure sketch and using a computational extractor \emph{sketch-and-comp-extract}.

Any improvement in computational extractors yields an improvement to the sketch-and-comp-extract construction of a computational fuzzy extractor.  Similarly, a computational fuzzy extractor is also a computational extractor~(ignoring the \rep functionality).  Thus, improving computational fuzzy extractors may improvement computational extractors.

The main advantage to analyzing the construction as a whole~(instead of sketch-and-comp-extract) is that security need not depend on the decoding radius $t$.  In sketch-and-comp-extract paradigm, the computational extractor must be able to handle sources with $\Hoo(W| \sketch(W))$.  As shown in \secref{sec:impossCompSecSketch}, this value depends on bounds from error-correcting codes.  In our construction, the decoding radius does not affect the security of the construction.  The decoding radius only impacts the running time of the decoding algorithm.  Conceivably, a computational fuzzy extractor could be built where only correctness depends on $t$~(not efficiency or security).
%However, the construction of a computational fuzzy extractor by 
%The advantage of \consref{cons:informal construction} is that losses due to error correction $O(\log |B_t(\cdot)|)$ and randomness extraction $O(\log 1/\epsilon)$ are not necessary.  In the case where $W$ is small, these losses may leave too few bits for a secure pseudorandom generator.  The work of~\cite{dachman2012computational} shows that these losses in the extract-then-expand construction are in some sense necessary~(the samplable RT conjecture in~\cite{dachman2012computational} has been resolved positively by~\cite{dodis2013key}).

@@

\section{Computational Fuzzy Exactor with Nonuniform Sources}
\label{sec:LWE block fixing sources}
In this section, we show the security of~\consref{cons:informal construction} is preserved for certain high entropy distributions.  Showing security of a computational fuzzy extractor for arbitrary high min-entropy distributions is an open problem.  First we recall the notion of a symbol fixing source~(from~\cite{KZ07}): 
\begin{definition}
Let $W = (W_1,..., W_{m+\alpha})$ be a distribution where $W_i$ takes values over $\{0,1\}^b$, we say that a distribution is a $m$-\emph{symbol fixing source} if $H_\infty(W)\geq mb$ and for all $W_i$ one of the following conditions is met:
\begin{itemize}
\item $W_i \overset{d}= U_b$
\item There exists a value $c_i$ such that $\Pr[W_i = c_i] =1$.
\end{itemize}
\end{definition}
%A block fixing source is an extension of a entropy source where each bit is independently random or fixed to larger alphabets.

We now study \consref{cons:informal construction} with a symbol fixing source.  Obviously, if $\alpha \geq n$ then the adversary knows $n$ equations and their error and $W$ can be recovered with Gaussian elimination.  We show that security degrades exponentially as symbols are fixed.
\ignore{
\begin{assumption}[LWE w/ entropic errors]
Let $n$ be a security parameter and define $m = \poly(n)$ and $q\geq 2$ be integers.  Let $W = W_1||...||W_{m+\alpha}$ be a $m$-block fixing distribution over $\{0,1\}^{(m+\alpha)\ell}$. For a vector 
Let $A\in\Fq^{(m+\alpha)\times (n+\alpha)}$ and let $x\in\Fq^{n+\alpha}$.  No PPT algorithm given $Ax+W$ can recover $x$ with probability greater than nonnegligible.
\end{assumption}
}
We now define the decisional $\LWE$ problem with symbol fixing errors is defined as follows: 
\begin{problem}[$\distLWE$ w/ symbol fixing errors]
Let $n$ be a security parameter and define $m = \poly(n)$ and $q\geq 2$ be integers.  Let $W = W_1||...||W_{m+\alpha}$ be a $m$-symbol fixing distribution over $\{0,1\}^{(m+\alpha)b}$. For a vector $X \leftarrow \Fq^n$, we denote $A_{X, W}$ be the distribution obtained by choosing a uniform $\vA\in\Fq^{(m+\alpha)\times (n+\alpha)}$ and outputting $\vA X + W$. The decisional learning with errors problem $\distLWE_{n+\alpha, m+\alpha, q, W}$ with symbol fixing errors is to distinguish samples chosen according $A_{X, W}$ for a uniformly random $X \in \Fq^{n+\alpha}$ from samples chosen according to the uniform distribution over $\Fq^{n+\alpha} \times \Fq$.
\end{problem}

The $\distLWE$ with symbol fixing sources is implied by standard $\distLWE$.
%\vspace{.1in}
\begin{theorem}
\label{thm:blockLWE}
Let $n$ be a security parameter and define $q, m , \alpha = \poly(n)$.  Let $\beta  = \omega(1)$, and $W$ be a $m$-symbol fixing source over $\{0,1\}^{(m+\alpha)b}$ where $\Hoo(W) \geq mb$.  The $\distLWE_{n, m,q, W}$ assumption implies the $\distLWE_{n+\alpha+\beta, m+\alpha, q, W}$ w/ symbol fixing sources problem.
\end{theorem}
We believe this statement is of interest outside our setting. \thref{thm:blockLWE} says that $\LWE$ is still secure when a small number of $\LWE$ samples have known errors.  Roughly, we need the number of variables larger than the number of equations with known error by letting the number of variables be the security parameter.  Providing a single sample with no error ``fixes'' at most a single variable.  Thus, if there are significantly more variables than samples with no error, search $\LWE$ should still be hard.  We are able to show~(a stronger result) that $\distLWE$ is still hard.  In the reduction, we argue that the additional $\alpha+ \beta$ variables allow us to explain a random value for the last $\alpha$ samples without knowledge of the other variables.  The $\beta$ parameter is the slack needed to ensure that the ``free'' variables have influence on the last $\alpha$ samples.  A formal proof is in \secref{sec:proof of block theorem}.

@@

\thref{thm:lossless block sketch log} is a direct consequence of \thref{thm:blockLWE} and parameter settings~(discussed in  \secref{ssec:block params}).  The weaker entropy source means we are able to extract fewer variables~($n/3$ instead of $n/2$) and that we must work over a slightly larger field.  We could set $\alpha$ larger than $n/3$ and extract fewer hardcore dimensions.  To extract enough bits and keep the field size polynomial in $n$, $n-\alpha$ must be at least a constant in $n$.  The parameter $\beta$ does not significantly impact the asymptotic behavior but is important for small values of $n$.

\ignore{
\subsection{\consref{cons:informal construction} with slightly deficient sources}
\label{sec:DP general error LWE}
In this section, we discuss how to generalize \consref{cons:informal construction} to an arbitrary high min-entropy distribution.  We will show security using a result of Micciancio and Peikert~\cite{micciancio2013hardness}.  This result allows us to argue security for an arbitrary distribution that is nearly high entropy.  This result should be seen as a complement to the proceeding sections.  It allows for a more general error distribution, but with worse parameters than \thref{thm:lossless secure conductor log}.  Also \thref{thm:lossless block sketch log} allows for more deficient sources but of a more restricted form~(symbol fixing sources).
\begin{theorem}
Let $n$ be a security parameter and let $m=cn, \ell = m-n/2$.  Let $C$ be a constant and define the parameter $\rho \geq (Cm)^{\frac{m-n/2}{n/2}} = (Cm)^{2c-1}$ and let $q$ be a prime where $\poly(n) = q\geq (4\rho)^{\frac{c}{c-1}}$.  Consider a distribution $\chi$ over the space $\{-\rho, ..., \rho \}^m$.  If $\Hoo(\chi)\geq m\log \rho$ and SIVP is hard to approximate in the worst case for quantum algorithms within an approximation factor of $\gamma=\tilde{O}(\sqrt{n} q)$~(on lattices of $n/2$ dimensions), then $\distLWE_{n, m, q, \chi}$ is $(\epsilon, s_{sec})\mbox{-}$secure, where $\epsilon = \ngl(n)$ for $s_{sec}=\poly(n)$.
\end{theorem}
\textbf{Note:}  The above theorem is a generalized version of~\cite[Theorem 4.6]{micciancio2013hardness}.  In particular, we note the requirement of sampling from the uniform distribution over some set $\chi \subset \{-\rho,..., \rho\}^m$ is not necessary.  The only requirement in the proof is that $|\chi|\geq m\log \rho$.  Requiring that $\Hoo(\chi) = m\log \rho$ implies that the support of $\chi$ contains at least $2^{m\log \rho}$ elements.  This theorem allows all distributions over a space of size $(2\rho)^m$ that have entropy at least $m\log \rho$.  This means we support all distributions whose entropy gap is no more than $m$ bits.

>>>>

\newcommand{\ve}{\vect{e}}
\newcommand{\vm}{\vect{m}}
\newcommand{\vy}{\vect{y}}
\newcommand{\vE}{\vect{E}}
\newcommand{\vS}{\vect{S}}
\newcommand{\vA}{\vect{A}}
\newcommand{\vc}{\vect{c}}
\newcommand{\vW}{\vect{W}}
\newcommand{\vR}{\vect{R}}
\newcommand{\vU}{\vect{U}}
\newcommand{\vT}{\vect{T}}
\newcommand{\vX}{\vect{X}}
\newcommand{\vB}{\vect{B}}
\newcommand{\vz}{\vect{z}}
\newcommand{\vd}{\vect{d}}
\newcommand{\vs}{\vect{s}}
\newcommand{\vx}{\vect{x}}
\newcommand{\va}{\vect{a}}
\newcommand{\vb}{\vect{b}}
\newcommand{\vgamma}{\mathbf{\Gamma}}
\newcommand{\vt}{\vect{t}}
\newcommand{\vu}{\vect{u}}
\newcommand{\vF}{\vect{F}}
\newcommand{\recout}{x}
\newcommand{\ignore}[1]{}
\newcommand{\M}{\mathcal{M}}

\title{\textbf{Computational Fuzzy Extractors}}
%\author{Benjamin Fuller%\footnote{The work of Benjamin Fuller is sponsored by the United States Air Force under Air Force Contract FA8721-05-C-0002. Opinions, interpretations, conclusions and recommendations are those of the authors and are not necessarily endorsed by the United States Government.}
% \and Xianrui Meng \and Leonid Reyzin}
\author{}
\begin{document}
\maketitle

@@

\item\textbf{Positive Result:} We show that the negative result can be overcome by
analyzing computational fuzzy extractors directly.  Namely, we show
how to build a computational fuzzy extractor whose output key length
equals the entropy of the source (this is impossible in the
information-theoretic setting). Our construction is based on the
hardness of the Learning with Errors (LWE) problem, and is secure when
the noisy source is uniform or symbol-fixing (that is, each dimension
is either uniform or fixed). As part of the security proof, we show a result of independent interest, namely
that the decision version of LWE is secure even when a small number of
dimensions has no error.
\end{itemize}
\textbf{Keywords} Fuzzy extractors, secure sketches, key derivation, Learning with Errors, error-correcting codes, computational entropy, randomness extractors.
\end{abstract}

\section{Introduction}\label{sec:introduction}

@@

\begin{theorem}
\label{thm:lossless secure extractor log}
Let $n$ be a security parameter and let $t = c\log n$ for some constant $c$.  Let $d\in \mathbb{Z}^+$ be a constant and consider the Hamming metric with block length $b = \log (2n^3 (c+2d)/d)$.  Let $W$ be uniform over $\zo^{(c+2d)nb/d}$.  If GAPSVP and SIVP are hard to approximate within polynomial factors~(on lattices of dimension $n/4$) using quantum algorithms, then there is a setting of $q = \poly(n)$ such that \consref{cons:informal construction} is a lossless fuzzy extractor.  That is, $H^{\hill}_{\epsilon, s_{sec}}(X_{1,..., n/2}|\vA, \vA X+W) = n/2\log q = H_\infty(W)$
% for following parameters:
%\[
%(\zo^{(c+d)/dn\log b}, |W|, \epsilon, s_{sec}, s_{sketch}, s_{rec}, t)
%\] 
with 
$\epsilon = \ngl(n), s_{sec} = \poly(n)$,  sketch runs in time $O(n^3\log n)$, and recover takes expected time $O(n^{4d+3} \log n)$ with error probability $\delta = e^{-\Omega(n)}$ over the choice of $\vA$.
\end{theorem}
\begin{proof}
Security follows by combining Lemmas~\ref{lem:uniform LWE decision} and~\ref{lem:many hardcore bits}, efficiency follows by \lemref{lem:i t poly time}.
\end{proof}

For a more detailed explanation of the various parameters and constraints see \secref{sec:parameter settings}.  In particular, we describe how to set $q = \poly(n)$.  
\thref{thm:lossless secure extractor log} shows that a computational fuzzy extractor can be built without incurring any entropy loss.  This is essentially due to $\vA X+W$ looking like a uniformly random point and providing no information about either $X$ or $W$.  
%A natural question to ask is whether security degrades gracefully when $W$ is not the uniform distribution.  We begin to provide an answer in \secref{sec:LWE block fixing sources}.

\subsection{Comparison with computational-extractor-based constructions}
\label{sec:prg based comparison}
As we already mentioned in the introduction, an alternative approach to building a computational fuzzy extractor is to use  a computational extractor (e.g.,~\cite{krawczyk2010cryptographic, barak2011leftover, dachman2012computational}) in place of the information-theoretic extractor in the sketch-and-extract construction.  We will call this approach \emph{sketch-and-comp-extract}.  (A simple example of a computational extractor is a pseudorandom generator applied to the output of an information-theoretic extractor; note that LWE-based pseudorandom generators exist~\cite{applebaum2006pseudorandom}.)
%using an information theoretic fuzzy extractor and then applying a pseudorandom generator to the output of the fuzzy extractor.  This is the extract-then-expand computational extractor suggested by Krawczyk in~\cite{krawczyk2010cryptographic}.

This approach (specifically, its analysis via \lemref{lem:fuzzy ext construction}) works as long as the amount of entropy $\tilde{m}$ of $w$ conditioned on the sketch $s$ remains high enough to run a computational extractor.  However, as discussed in \secref{sec:impossCompSecSketch}, $\tilde{m}$ decreases with the error parameter $t$ due to coding bounds, and it is conceivable that, if $W$ has  barely enough entropy to begin with, it will have too little entropy left to run a computational extractor once $s$ is known.

In contrast, our approach does not require the entropy of $w$ conditioned on $p=(\vA, \vA X+w)$ to  be high enough for a computational extractor. Instead, we require that $w$ is not computationally recoverable  given $p$.  This requirement is weaker.  The key difference in our approach is that instead of extracting from $w$, we hide secret randomness using $w$. Computational extractors are not allowed to have private randomness \cite[Definition 3]{krawczyk2010cryptographic}.

The main advantage of our analysis (instead of sketch-and-comp-extract) is that security need not depend on the error-tolerance $t$.  Our codes (namely, random linear codes) can tolerate higher $t$ than can be efficiently decoded.  In the case of secure sketches, codes tolerating such high $t$ would leave little entropy in $w$.  In our construction, the error-tolerance depends only on the best available decoding algorithm for random linear codes.

Unfortunately, LWE parameter sizes require relatively long $w$. Therefore, in practice, sketch-then-comp-extract will beat our construction  if the computational extractor is instantiated efficiently based on assumptions other than LWE (for example, a cryptographic hash function for an extractor and a block cipher for a PRG). However, we believe that our conceptual framework can lead to better constructions.  Of particular interest are  other codes that are easy to decode up to $t$ errors but become computationally hard as the number of errors increases.

%However, the construction of a computational fuzzy extractor by 
%The advantage of \consref{cons:informal construction} is that losses due to error correction $O(\log |B_t(\cdot)|)$ and randomness extraction $O(\log 1/\epsilon)$ are not necessary.  In the case where $W$ is small, these losses may leave too few bits for a secure pseudorandom generator.  The work of~\cite{dachman2012computational} shows that these losses in the extract-then-expand construction are in some sense necessary~(the samplable RT conjecture in~\cite{dachman2012computational} has been resolved positively by~\cite{dodis2013key}).

@@

\section{Computational Fuzzy Extractor for Nonuniform Sources}
\label{sec:LWE block fixing sources}
While showing the security of~\consref{cons:informal construction} for arbitrary high-min-entropy distributions is an open problem, in this section we show it for a particular class of distributions called symbol-fixing.  First we recall the notion of a symbol fixing source~(from~\cite{KZ07}): 
\begin{definition}
Let $W = (W_1,..., W_{m+\alpha})$ be a distribution where $W_i$ takes values over $\{0,1\}^b$, we say that a distribution is a $m$-\emph{symbol fixing source} if $H_\infty(W)\geq mb$ and for all $W_i$ one of the following conditions is met:
\begin{itemize}
\item $W_i \overset{d}= U_b$
\item There exists a value $c_i$ such that $\Pr[W_i = c_i] =1$.
\end{itemize}
\end{definition}
%A block fixing source is an extension of a entropy source where each bit is independently random or fixed to larger alphabets.

\ignore{
We now study \consref{cons:informal construction} with a symbol fixing source.

\begin{assumption}[LWE w/ entropic errors]
Let $n$ be a security parameter and define $m = \poly(n)$ and $q\geq 2$ be integers.  Let $W = W_1||...||W_{m+\alpha}$ be a $m$-block fixing distribution over $\{0,1\}^{(m+\alpha)\ell}$. For a vector 
Let $A\in\Fq^{(m+\alpha)\times (n+\alpha)}$ and let $x\in\Fq^{n+\alpha}$.  No PPT algorithm given $Ax+W$ can recover $x$ with probability greater than nonnegligible.
\end{assumption}
}
We now define the decisional $\LWE$ problem with symbol fixing errors: 
\begin{problem}[$\distLWE$ w/ symbol fixing errors]
Let $n$ be a security parameter and define $m = \poly(n)$ and $q\geq 2$ be integers.  Let $W = W_1||...||W_{m+\alpha}$ be a $m$-symbol fixing distribution over $\{0,1\}^{(m+\alpha)b}$. For a vector $X \leftarrow \Fq^n$, we denote $A_{X, W}$ be the distribution obtained by choosing a uniform $\vA\in\Fq^{(m+\alpha)\times (n+\alpha)}$ and outputting $\vA X + W$. The decisional learning with errors problem $\distLWE_{n+\alpha, m+\alpha, q, W}$ with symbol fixing errors is to distinguish samples chosen according $A_{X, W}$ for a uniformly random $X \in \Fq^{n+\alpha}$ from samples chosen according to the uniform distribution over $\Fq^{n+\alpha} \times \Fq$.
\end{problem}

The following theorem states the main technical result of this section, which is of potential interest outside our specific setting. The result is that $\distLWE$ with symbol-fixing sources is implied by standard $\distLWE$,  with security degrading exponentially as symbols are fixed (of course, once $n$ symbols are fixed, no security remains, because there are $n$ linear equations with known error and $n$ unknowns).
%\vspace{.1in}
\begin{theorem}
\label{thm:blockLWE}
Let $n$ be a security parameter and define $q, m , \alpha = \poly(n)$.  Let $\beta  = \omega(1)$, and $W$ be a $m$-symbol fixing source over $\{0,1\}^{(m+\alpha)b}$ where $\Hoo(W) \geq mb$.  The $\distLWE_{n, m,q, W}$ assumption implies the $\distLWE_{n+\alpha+\beta, m+\alpha, q, W}$ w/ symbol fixing sources problem.
\end{theorem}

The intuition for this result is as follows.  Providing a single sample with no error ``fixes'' at most a single variable.  Thus, if there are significantly more variables than samples with no error, intuitively search $\LWE$ should still be hard.  We are able to show a stronger result that $\distLWE$ is still hard.  The nontrivial part of the reduction is using the additional $\alpha+ \beta$ variables  to ``explain'' a random value for the last $\alpha$ samples, without knowing the other variables.  The $\beta$ parameter is the slack needed to ensure that the ``free'' variables have influence on the last $\alpha$ samples.  A formal proof is in \secref{sec:proof of block theorem}.

@@

\thref{thm:lossless block sketch log} is a direct consequence of \thref{thm:blockLWE} and parameter settings~(discussed in  \secref{ssec:block params}).  The weaker entropy source means we are able to extract fewer variables~($n/3$ instead of $n/2$) and that we must work over a slightly larger field.  We could set $\alpha$ larger than $n/3$ and extract fewer hardcore dimensions.  To extract enough bits and keep the field size polynomial in $n$, $n-\alpha$ must be at least a constant fraction of $n$.  The parameter $\beta$ does not significantly impact the asymptotic behavior but is important for small values of $n$.

\ignore{
\subsection{\consref{cons:informal construction} with slightly deficient sources}
\label{sec:DP general error LWE}
In this section, we discuss how to generalize \consref{cons:informal construction} to an arbitrary high min-entropy distribution.  We will show security using a result of Micciancio and Peikert~\cite{micciancio2013hardness}.  This result allows us to argue security for an arbitrary distribution that is nearly high entropy.  This result should be seen as a complement to the proceeding sections.  It allows for a more general error distribution, but with worse parameters than \thref{thm:lossless secure extractor log}.  Also \thref{thm:lossless block sketch log} allows for more deficient sources but of a more restricted form~(symbol fixing sources).
\begin{theorem}
Let $n$ be a security parameter and let $m=cn, \ell = m-n/2$.  Let $C$ be a constant and define the parameter $\rho \geq (Cm)^{\frac{m-n/2}{n/2}} = (Cm)^{2c-1}$ and let $q$ be a prime where $\poly(n) = q\geq (4\rho)^{\frac{c}{c-1}}$.  Consider a distribution $\chi$ over the space $\{-\rho, ..., \rho \}^m$.  If $\Hoo(\chi)\geq m\log \rho$ and SIVP is hard to approximate in the worst case for quantum algorithms within an approximation factor of $\gamma=\tilde{O}(\sqrt{n} q)$~(on lattices of $n/2$ dimensions), then $\distLWE_{n, m, q, \chi}$ is $(\epsilon, s_{sec})\mbox{-}$secure, where $\epsilon = \ngl(n)$ for $s_{sec}=\poly(n)$.
\end{theorem}
\textbf{Note:}  The above theorem is a generalized version of~\cite[Theorem 4.6]{micciancio2013hardness}.  In particular, we note the requirement of sampling from the uniform distribution over some set $\chi \subset \{-\rho,..., \rho\}^m$ is not necessary.  The only requirement in the proof is that $|\chi|\geq m\log \rho$.  Requiring that $\Hoo(\chi) = m\log \rho$ implies that the support of $\chi$ contains at least $2^{m\log \rho}$ elements.  This theorem allows all distributions over a space of size $(2\rho)^m$ that have entropy at least $m\log \rho$.  This means we support all distributions whose entropy gap is no more than $m$ bits.
